---
title: "Getting a Gig"
author: "Sean Corcoran, Sarah Dodamead, Christopher Matos, Ethan Tenison"
date: "3/9/2020"
output: html_document
---

```{r libraries, message=FALSE, warning=FALSE}

list.of.packages <-
        c(
                "tidyverse",
                "googledrive",
                "janitor",
                "dplyr",
                "caret"
                
                
           )

new.packages <-list.of.packages[!(list.of.packages %in% installed.packages()[, "Package"])]


library(googledrive)
library(tidyverse)
library(janitor)
library(dplyr)
library(caret)

```

## Pulling in the data 

```{r data, cache = TRUE}

 drive_download(as_id("1S4B1Txs-ycsyO0X6DEA5C1STHt1fXeOK"), overwrite = TRUE)
 data <- read.csv("EER396_Data_Set.csv")
 data <- clean_names(data)
 str(data)


```


## Data Cleaning 

#### Variables that have been removed: 
-da_activated
-background_submit_Date
-submit_profile_time
-orientation_selection_time
-orientation_start_time (we need to check to see if this is valueable)
-waitlist_end_date  (this would be more helpful if we knew what date they were put on a waitlist)
-mvr_initiated  
-mvr_cleared 
-criminal_initiated
-criminal_cleared
-dropship_kit_ordered
-orient_date
-start_date  this is connected to activation which we also deleted 
-first_dash_date, this is removed after the converted variable is created 
-planned_time 
-apply_date (this value is important if we need to calculate new day variables)
-applied_submarket
-planned_sp
-planned_sm 
-offer_end
-NA's were removed from submit_profile_time because we don't have enough data on individuals who haven't made it past that step. 

#### Variables that have been created: 
-converted, binary variable describing if a lead has converted or not




```{r datacleaning}


df <- data %>% mutate(converted = ifelse(!is.na(data$first_dash_date), 1, 0)) %>% 
        filter(!is.na(submit_profile_time)) %>% 
        select(-c("da_activated", "background_submit_date", "submit_profile_time", "orientation_selection_time","orientation_start_time", "mvr_initiated","mvr_cleared",
                  "criminal_initiated","criminal_cleared", "orient_date", "start_date", "first_dash_date", "planned_time", "waitlist_end_date" ,"dropship_kit_ordered","apply_date",
                  "applied_submarket","planned_sp", "planned_sm", "offer_end" )) 
        
        

```


## Logistic Regression

```{r logistic_regression}
# da_mvr_bgc_start + da_mvr_bgc_pass +

logit <- glm(converted ~ age + orientation_type + channel + da_profile_submit + da_orientation_select
             + da_dropshipping_created + da_oriented + holdout, data = df, family = "binomial")

summary(logit)


```
